% cover.tex - My Cover letter template using letter.sty
\documentclass{letter}
\topmargin=-1in
\textheight=8in
\oddsidemargin=0pt
\textwidth=6.5in
\usepackage{fontspec, hyperref}
\setmainfont{Palatino}

\begin{document}

\signature{Parker J Pinette}
\longindentation=8pt
\let\raggedleft\raggedright
\headsep=20pt

\begin{letter}{}

\begin{flushleft}
 {\large\bf Parker J Pinette}
\end{flushleft}
\medskip\hrule height 1pt
\begin{flushright}
 \hfill \href{mailto:parker@parkerpinette.com}{parker@parkerpinette.com}, (801) 638-8611, \url{https://github.com/ppinette} 
\end{flushright}
\vfill

\opening{Dear Hiring Manager:}

\noindent Your job posting for <insert job here> caught my eye, and I believe I would be a good candidate for the position.  

\noindent I've worked in various IT disciplines for over 10 years, from tech support and system building to system administration. I've dabbled in web development since high school, but for the last couple years I've made it my main focus. I have a solid grasp of Python, which I began using for shell scripting during my time at the University of Utah. Since then I've used it extensively in web projects via the Pyramid Web Framework. I love programming in Python, and I'm always excited to expand my skills. 

\noindent I've been using HTML and CSS since high school, and have a firm understanding of web development principles. While I was never an expert with Javascript, I have comfortable writing it and have been using jQuery plugins and my own one-liners fairly extensively in recent projects. 

\noindent I feel that these skills, along with my background in system administration make me well suited for a variety of roles. I see myself as a budding full-stack developer; I'm as happy writing object relational models as I am fine tuning CSS media queries. I'm always looking to add to my skillset and improve my knowledge. I actively commit to my various Github projects, and prowl other projects for ways to contribute.

\noindent I believe I could be an asset to your team, if given the opportunity. I'd love to be considered for an in-person interview. I look forward to hearing from you.

\closing{Sincerely,}
\end{letter}

\end{document}
