% ParkerJPinette.tex - My resume using res.cls (http://www.rpi.edu/dept/arc/training/latex/resumes/)
\documentclass[line,margin]{res}
\usepackage{fontspec, hyperref}
\setmainfont{Palatino}

\begin{document}

\name{Parker J Pinette}\date{\today}
\address{\href{mailto:parker@parkerpinette.com}{parker@parkerpinette.com} \\ (801) 638-8611 \\ \url{https://github.com/ppinette}}

\begin{resume}

%\section{CAREER OBJECTIVE}To find a full time position working with Python, ideally utilizing my background in system administration and web development.

\section{EXPERIENCE}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 {\bf Web Developer - Self-Employed - Emeryville, CA} \hfill 2011-Present\\
 %{\sl Emeryville, CA }\\
 {\sl Freelance web developer focusing on the Pyramid Web Framework. Some notable public-facing projects include:}
  \begin{itemize} \itemsep -2pt % reduce space between items
  \item \url{http://fincaslc.com}  % use [] to prevent bullet from printing
  \item \url{http://imatterutah.org}
  \end{itemize}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 {\bf IT/System Administrator - University of Utah - SLC, UT} \hfill 2007-2011\\
 %{\sl Salt Lake City, UT }\\
 {\sl Extensive heterogeneous environment spanning 7 buildings, 1300 nodes, gigabit Ethernet, fiber uplinks, 1200 active users. Full range of services including Unix shell and X application, Terminal Services, Active Directory, Web hosting, network file services (NFS, SMB, AFP), backup (Netbackup), workstation deployment, patch management, distributed power management. Staff of 7. My personal responsibilities included:}
   \begin{itemize} \itemsep -2pt
   \item Configuring, maintaining, and supporting all Linux and Mac-based hosts.
   \item Configuring and maintaining SPARC-based servers running Solaris 8 and 10.
   \item Compiling application tree for web and other network services
   \item Editing DNS zone files – cleaning up old entries
   \item MySQL – managing several instances. Replication/backup. 
   \item Configuring and managing centralized logging with Syslog and Syslog-ng.
   \item Monitoring and alerts using Nagios and Zabbix.
   \item User and group management (originally in NIS+, transitioning to LDAP/AD).
   \item Supporting NT servers as needed (AD, terminal services, Exchange).
   \item Desktop support and deployment as needed (WinXP, Win7).
   \item Remote management of servers and workstations using SSH, RDP, and VNC.
   \item Frontend web development in TikiWiki, Joomla, and Dreamweaver-based sites.
   \item Debugging old PHP code - custom and open source CMS
   \item Supervising and delegating to technical assistants.
   \end{itemize}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 {\bf IT Consultant - JP Tech - SLC, UT} \hfill 2004-2008\\
 %{\sl Salt Lake City, UT }\\
 {\sl I opened an IT consulting firm serving small businesses and home office users.}
  \begin{itemize} \itemsep -2pt
  \item Providing a full range of IT services in Salt Lake City and Phoenix.    
  \item Supporting Windows XP desktops and Linux(Gentoo, Ubuntu) servers.
  \item Web design, development, and hosting.
  \item Custom web applications.
  \end{itemize}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{SKILLS}
 \begin{description} \itemsep -2pt
 \item[Development:] Python, JavaScript, exposed to PHP, C++
 \item[Web:] HTML, CSS/SASS, jQuery
 \item[Frameworks:] Pyramid, Zurb Foundation, exposed to Drupal, Joomla, Wordpress
 \item[Operating Systems:] Linux(Debian, Ubuntu), Solaris, FreeBSD, OS X, Windows < 8
 \item[Services:] Apache, Nginx, uWSGI
 \item[Environments:] Vim, exposed to Aptana, Dreamweaver 
 \item[Design:] Photoshop, exposed to full CS6 Suite
 \item[Markup:] Mako, \LaTeX
 \item[Misc:] Git, Firebug, WebKit Web Inspector
 \end{description}
					
\section{EDUCATION}
 {\sl Lone Peak High School - 2000} - General/Technical Studies\\
 {\sl University of Utah} - General Studies

\end{resume}
\end{document}
